### 2018-04-05 paper/algorithm.tex
Adds pointers to GitHub issues

All swarms participate in the Inter-Swarm Protocol to coordinate the global 
knowledge needed by the swarms to interact.
More specifically, the global knowledge contains:
\begin{itemize}
  \item A table, \(R\), of devices available for routing.
  \item A key--value store, \(S\colon \{0, 1\}^\lambda\to \{0, 1\}^*\), mapping 
    fixed-length strings of length \(\lambda\) to arbitrary-length strings.
    We will use the notation \(x\mapsto S[x]\).
\end{itemize}

>>>>

All swarms participate in the Inter-Swarm Protocol to coordinate the global 
knowledge needed by the swarms to interact.
More specifically, the global knowledge contains:
\begin{itemize}
  \item A table, \(R\), of devices available for routing;
  \item A key--value store, \(S = \{0, 1\}^\lambda\times \{0, 1\}^*\), mapping 
    fixed-length strings of length \(\lambda\) to arbitrary-length strings.
\end{itemize}

### 2018-04-05 paper/intro.tex

It is common nowadays to use a third party, i.e.\ someone else's computer (better 
known as the Cloud), as an intermediate to share files.
For instance, it is common for Alice to upload a file to e.g.\ Box, Dropbox or 
OneDrive and share the link with Bob who can then download it.
The goal of this work is to design a decentralized, distributed system where 
Alice can share files \emph{effortlessly} between her own devices, e.g.\ laptop, 
smartphone and tablet.
But Alice should also be able to use her smartphone to share a file on her home 
computer with Bob.
Since these are Alice's private devices, privacy is essential.
E.g.\ it would be devastating for Alice's privacy if Bob could stalk her by 
tracking her devices or discern usage patterns.

>>>>

It is common nowadays to use a third party, \ie someone else's computer (better 
known as the Cloud), as an intermediate to share files.
For instance, it is common for Alice to upload a file to \eg Box, Dropbox or 
OneDrive and share the link with Bob who can then download it.
The goal of this work is to design a decentralized, distributed system where 
Alice can share files \emph{effortlessly} between her own devices, \eg laptop, 
smartphone and tablet.
But Alice should also be able to use her smartphone to share a file on her home 
computer with Bob.
Since these are Alice's private devices, privacy is essential.
E.g.\ it would be devastating for Alice's privacy if Bob could stalk her by 
tracking her devices or discern usage patterns.

### 2018-04-05 paper/related.tex

Firstly, fields studies provide \emph{usage and connectivity patterns of users' appliances}.
Karlson et al. \cite{Karlson_Meyers_Jacobs_Johns_Kane_2009} studied the compared usage of the laptop and smartphone of 16 information workers: 
they show that their participants use their smartphones very regularly throughout the day to do background tasks (e.g. answering mails or checking their agenda).
Their laptop is online less often, and is dedicated to the most demanding tasks.
Wagner et al. \cite{Wagner_Rice_Beresford_2013} conducted a thorough data collection on Android devices via an application called Device Analyzer, that collected metrics on movement patterns, connectivity and energy consumption from 16,000 users.
\commentAL{Conclude: will we use their dataset? Why are these papers useful to us?}

@@

Finally, research in P2P networks observed \cite{Stutzbach_Rejaie_2006} and modeled \cite{Yao_Leonard_Wang_Loguinov_2006} patterns of \emph{churn} (i.e. participants moving in and out of a system).

>>>>

Firstly, fields studies provide \emph{usage and connectivity patterns of users' appliances}.
Karlson et al. \cite{Karlson_Meyers_Jacobs_Johns_Kane_2009} studied the compared usage of the laptop and smartphone of 16 information workers: 
they show that their participants use their smartphones very regularly throughout the day to do background tasks (\eg answering mails or checking their agenda).
Their laptop is online less often, and is dedicated to the most demanding tasks.
Wagner et al. \cite{Wagner_Rice_Beresford_2013} conducted a thorough data collection on Android devices via an application called Device Analyzer, that collected metrics on movement patterns, connectivity and energy consumption from 16,000 users.
\commentAL{Conclude: will we use their dataset? Why are these papers useful to us?}

@@

Finally, research in P2P networks observed \cite{Stutzbach_Rejaie_2006} and modeled \cite{Yao_Leonard_Wang_Loguinov_2006} patterns of \emph{churn} (\ie participants moving in and out of a system).

### 2018-04-05 paper/user-model.tex

% P\left[o^{(d)}_{t+i}=1 \mid S_{t} \right] = \sum\limits_{s \in \mathcal{S}} P\left[ S_{t+1}=s \mid S_t\right] * P\left[o^{(d)}_{t+i}=1 \mid S_{t+1}=s \right]
% \end{multline}

>>>>

\Cref{fig:sample_usage} plots a sample device usage timeline using the previous model. 
Each device starts offline; the user can toggle one device per round (or do nothing).
In this figure, we show the device \emph{usage}, that is a consequence of the $\mathit{toggle}$ events defined by the HMM.
As a consequence, several devices can be online at the same time, as happens in the figure.
